Detecting AI-Generated Images using ResNet

### 2022-12-14 paper/paper.tex
Update paper

@@

The models have shown surprisingly good results with the comic book dataset where both the synthetic images and the original images are not camera-captured photos and also very different from the training dataset in styles and themes. The fact that the models generalize fairly well on this dataset indicates that the model may have learned some general features of the synthetic images that are from the Stable Diffusion model. But the much worse performance from the two models on the DALL·E-2-generated datasets indicates that the features the models have learned are very specific to the Stable Diffusion model and not generalizable to other models, even when those models are also based on diffusers. To human eyes, DALL·E 2 do generate more realistic and detailed images compared to the Stable Diffusion model. From the comparison of the confusion matrices shown in Figure \ref{fig:paper_training_confusion_matrix} and Figure \ref{fig:paper_dalle2_weather_confusion_matrix}, we can see that for the validation split for the main dataset that we trained on, the models predicted rather balanced results. However, the models are more likely to predict the DALL·E-2 generated images as original images thinking that they are real photos.

>>>>

Resnet-34 involves the insertion of shortcut connections in turning a plain network into its residual network counterpart. In this case, the plain network was inspired by VGG neural networks (VGG-16, VGG-19), with the convolutional networks having 3×3 filters. However, compared to VGGNets, ResNets have fewer filters and lower complexity. The 34-layer ResNet achieves a performance of 3.6 bn FLOPs, compared to 1.8bn FLOPs of smaller 18-layer ResNets.

@@

The models have shown surprisingly good results with the comic book dataset where both the synthetic images and the original images are not camera-captured photos and also very different from the training dataset in styles and themes. The fact that the models generalize fairly well on this dataset indicates that the model may have learned some general features of the synthetic images that are from the Stable Diffusion model. But the much worse performance from the two models on the DALL·E-2-generated datasets indicates that the features the models have learned are very specific to the Stable Diffusion model and not generalizable to other image-generation models, even when those models are also based on diffusers. To human eyes, DALL·E 2 do generate more realistic and detailed images compared to the Stable Diffusion model. From the comparison of the confusion matrices shown in Figure \ref{fig:paper_training_confusion_matrix} and Figure \ref{fig:paper_dalle2_weather_confusion_matrix}, we can see that for the validation split for the main dataset that we trained on, the models predicted rather balanced results. However, the models are more likely to predict the DALL·E-2 generated images as original images thinking that they are real photos.
